Current status and propsects of R-packages for the design of experiments

### 2021-02-07 paper.tex
initial with analysis from blog

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{graphicx}

\title{Capitalized Title Here}

\author{
    Emi Tanaka
    \thanks{emitanaka.org}
   \\
    Department of Econometrics and Business Statistics \\
    Monash University \\
  Clayton, VIC 3800 \\
  \texttt{\href{mailto:emi.tanaka@monash.edu}{\nolinkurl{emi.tanaka@monash.edu}}} \\
  }

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

% Pandoc citation processing

\begin{document}
\maketitle

\def\tightlist{}

\begin{abstract}
An abstract of less than 150 words.
\end{abstract}

@@

Introductory section which may include references in parentheses
({\textbf{???}}), or cite a reference such as ({\textbf{???}}) in the
text.

@@

@@

\begin{figure}[htbp]

@@

\caption{The logo of R.}\label{fig:Rlogo}
\end{figure}

\hypertarget{another-section}{%
\subsection{Another section}\label{another-section}}

There will likely be several sections, perhaps including code snippets,
such as:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{x \textless{}{-}}\StringTok{ }\DecValTok{1}\OperatorTok{:}\DecValTok{10}
\KeywordTok{plot}\NormalTok{(x)}
\end{Highlighting}
\end{Shaded}

\includegraphics{arxiv_files/figure-latex/unnamed-chunk-3-1.pdf}

@@

\bibliographystyle{unsrt}
\bibliography{references.bib}

\end{document}

>>>>

% !TeX root = RJwrapper.tex
\title{Current status and propsects of R-packages for the design of
experiments}
\author{by Emi Tanaka}

\maketitle

\abstract{%
An abstract of less than 150 words.
}

\begin{Schunk}
\begin{table}

\caption{\label{tab:bigram-title}The bigram of the R-package titles as provided in the DESCRIPTION file in CRAN.}
\centering
\begin{tabular}[t]{l|r}
\hline
Bigram & Count\\
\hline
optimal design & 10\\
\hline
experimental design & 8\\
\hline
clinical trial & 5\\
\hline
dose finding & 5\\
\hline
sequential design & 5\\
\hline
block design & 4\\
\hline
microarray experiment & 4\\
\hline
response surface & 4\\
\hline
\end{tabular}
\end{table}

\end{Schunk}

\begin{Schunk}
\begin{table}

\caption{\label{tab:bigram-desc}The bigram of the R-package descriptions as provided in the DESCRIPTION file in CRAN.}
\centering
\begin{tabular}[t]{lr}
\toprule
Bigram & Count\\
\midrule
experimental design & 11\\
optimal design & 10\\
package provide & 7\\
response surface & 7\\
factorial design & 6\\
\addlinespace
graphical user & 6\\
user interface & 6\\
block design & 5\\
contour plot & 5\\
design based & 5\\
\addlinespace
effect model & 5\\
fractional factorial & 5\\
microarray experiment & 5\\
mixed effect & 5\\
provide function & 5\\
\addlinespace
sample size & 5\\
sequential design & 5\\
\bottomrule
\end{tabular}
\end{table}

\end{Schunk}

\begin{Schunk}
\begin{Soutput}
#> `stat_bin()` using `bins = 30`. Pick better value with `binwidth`.
\end{Soutput}

\begin{center}\includegraphics{paper_files/figure-latex/download-hist-1} \end{center}

\end{Schunk}

\begin{Schunk}

\begin{center}\includegraphics{paper_files/figure-latex/download-barplot-1} \end{center}

\end{Schunk}

\begin{Schunk}

\begin{center}\includegraphics{paper_files/figure-latex/download-timeplot-1} \end{center}

\end{Schunk}

@@

\texttt{test} \code{test}

\CRANpkg{agricolae}

\ctv{ExperimentalDesign}

\ctv{OfficialStatistics}

\hypertarget{helping-info-to-get-started}{%
\subsection{Helping info to get
started}\label{helping-info-to-get-started}}

Introductory section which may include references in parentheses
\citep{R}, or cite a reference such as \citet{R} in the text.

@@

Let's check fi this works Figure @ref(fig:Rlogo).

@@

\begin{Schunk}
\begin{figure}[htbp]

@@

\caption[The logo of R]{The logo of R.}\label{fig:Rlogo}
\end{figure}
\end{Schunk}

@@

\bibliography{paper.bib}

\address{%
Emi Tanaka\\
Monash University\\%
Monash University\\ Clayton campus, VIC 3800, Australia\\
%
\url{http://emitanaka.org/}%
\\\textit{ORCiD: \href{https://orcid.org/0000-0002-1455-259X}{0000-0002-1455-259X}}%
\\\href{mailto:emi.tanaka@monash.edu}{\nolinkurl{emi.tanaka@monash.edu}}
}
